\documentclass[a4paper,12pt]{article}
%\documentclass[a4paper,10pt]{scrartcl}

\usepackage[utf8x]{inputenc}
\usepackage{amsfonts}
\usepackage{amsmath,esint}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage{sansmath}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{caption}

\usepackage{tikz}


\definecolor{boiseBlue} {RGB}{29,72,159}
\definecolor{rojoAmor} {RGB}{171,13,4}
\definecolor{moradoAmor} {RGB}{93,8,113}
\definecolor{verdeAmor} {RGB}{98,158,31}
\definecolor{negro} {RGB}{10,10,10}
\definecolor{lgreen} {RGB}{180,210,100}
\definecolor{dblue}  {RGB}{20,66,129}
\definecolor{ddblue} {RGB}{11,36,69}
\definecolor{lred}   {RGB}{220,0,0}
\definecolor{nred}   {RGB}{224,0,0}
\definecolor{norange}{RGB}{230,120,20}
\definecolor{nyellow}{RGB}{255,221,0}
\definecolor{ngreen} {RGB}{98,158,31}
\definecolor{dgreen} {RGB}{78,138,21}
\definecolor{nblue}  {RGB}{28,130,185}
\definecolor{jblue}  {RGB}{20,50,100}

\usepackage{listings}
\usepackage{xcolor}
\usepackage{verbatim}
\lstset{language=C++,
		basicstyle=\ttfamily,
	       backgroundcolor=\color{black!5}\ttfamily,
                keywordstyle=\color{nblue}\ttfamily,
                stringstyle=\color{nred}\ttfamily,
                commentstyle=\color{ngreen}\ttfamily,
                morecomment=[l][\color{moradoAmor}]{\#}
}

\newenvironment{rcases}{\left.\begin{aligned}}{\end{aligned}\right\rbrace}

\renewcommand{\familydefault}{\sfdefault}

\newcommand{\specialcell}[2][c]{%
  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
% \specialcell{Foo\\bar}

\title{Modeling 2.5d with 2d PDE solvers\\{\normalsize for wave and dc energy transfers}\\{\normalsize Diego Domenzain}}
\author{}
\date{}

\pdfinfo{%
  /Title    ()
  /Author   ()
  /Creator  ()
  /Producer ()
  /Subject  ()
  /Keywords ()
}

\begin{document}
\maketitle
%-------------------
% main flow
%-------------------
\section*{2.5d nature and 2d numerical code}
We assume that in nature there is no lateral variation along the $y$ axis $(\partial_y=0)$. Because the $xz$-plane is embedded in $xyz$-space, the energy transfer is not truly 2d and so we refer to this assumption as ``2.5d", i.e. we assume nature transfers energy in 2.5d.
\\\\
We note that even though under the assumption $\partial_y=0$ the energy transfer is 2.5d, all the relevant information of the material properties is 2d and lies in the $xz$-plane.
\\\\
Numerically it is less computationally expensive to model 2d rather than 3d phenomena, therefore we either have to transform observed 2.5d data ($d^o$) into 2d data ($d_{2d}^o$) or conversely, transform the 2d synthetic field $u_{2d}$ to a 2.5d field $u$. Table \ref{tbl:2d25d} gives quick reference to the methods used for both wave and dc energy transfers.
\begin{table}[!h]
\begin{tabular}{ c | c c c | c }
  & nature &  & code & transform \\
  \hline
wave & 2.5d & $\to$ & 2d & $\tilde{d}_{2d}^o = \sqrt{ \frac{2\pi v_o\,\Delta sr}{|\omega|} }
\exp\left\{{\frac{\imath}{4} \operatorname{sgn} (\omega)}\right\}\,\tilde{d}^o$ \\
 dc & 2.5d& $\gets$ & 2d & $u=\sum_i w_i u_{2d}^i$ \\
\end{tabular}
\caption{Quick 2d-2.5d transform reference table.}
 \label{tbl:2d25d}
\end{table}
% ----------------------------
% 2.5d wave
% ----------------------------
\section*{2.5d wave solver}
For the wave energy transfer, we observe data in 2.5d, we solve the governing PDE in 2d, and we transform the observed data into 2d. We follow \cite{bleistein1986two} and \cite{ernst2007application}. 
\\\\
Let $u=u(x,y,z,t,v_o; \, s)$ be the 2.5d wavefield on the $xyz$-space at time $t$ due to a source $s=(s_x,0,s_z,t)$ and a constant velocity $v_o$. Let $u_{2d}$ be the 2d wave solved numerically, then the 2.5d$\to$2d transform is given by,
\begin{align}
\tilde{u}_{2d} &= \sqrt{ \frac{2\pi v_o\,\Delta sr_{xz}}{|\omega|} }
\exp\left\{{\frac{\imath}{4} \operatorname{sgn} (\omega)}\right\}\,\tilde{u},
\end{align}
where $\omega$ is angular frequency and $\Delta sr_{xz}$ is distance between source and a point $(x,0,z)$. 
\\\\
This 2d$\to$2.5d asymptotic conversion assumes isotropic media, is valid in the high frequency eikonal regime, and does not take intrinsic attenuation into account.
\\\\
In practice we only perform this transform on the observed data, i.e. only on receiver locations $r$ and we approximate $v_o$ with the average of the heterogeneous velocity model $v$,
\begin{align}
\tilde{d}_{2d}^o = \sqrt{ \frac{2\pi v_o\,\Delta sr}{|\omega|} }
\exp\left\{{\frac{\imath}{4} \operatorname{sgn} (\omega)}\right\}\,\tilde{d}^o.
\label{eq:w2d}
\end{align}
\subsection*{2d inversion}
After transforming the 2.5d observed data into 2d, we proceed with the inversion by minimizing the error $e=d_{2d}^{o}-d$ where $d$ is the synthetic data. This transform is performed only once before the inversion and never again.
\\\\
The imaged parameters after the inversion will be in 2d, which in the case of material properties 2d is also 2.5d. 
\subsection*{Routines}
\begin{itemize}
\item \color{boiseBlue}\texttt{w\_bleistein.m}\color{black}
\begin{align*}
\tilde{b} &= \sqrt{ \frac{1}{|f|} }
\exp\left\{{\frac{\imath}{4} \operatorname{sgn} (f)}\right\} \cdot \sqrt{\Delta sr}.
\end{align*}
$\tilde{b}$ is a matrix of size $(n_f\times n_r)$ and $f$ is the frequency discretization.
\item \color{boiseBlue}\texttt{w\_2\_5d\_2d.m}\color{black}
\\\\
Takes $d_w^o$ and $\tilde{b}$ and performs the Bleistein filter in the frequency domain but returns $d_w^o$ in the time domain.
\end{itemize}
% ----------------------------
% 2.5d dc
% ----------------------------
\section*{2.5d dc solver}
For the dc energy transfer, we observe data in 2.5d, we solve many (more than one at least) governing PDEs in 2d, and we transform these 2d solutions into 2.5d. We follow \cite{pidlisecky2008fw2_5d}.
\\\\
In 2.5d, we want to model
\begin{align}
-\nabla\cdot\sigma(x,z)\nabla\,u(x,y,z) &= s(x,y,z).
\label{eqn:dc-2-5d}
\end{align}
In the Fourier $k_y$-domain we have,
\begin{align}
-2\nabla\cdot\sigma\nabla\,\tilde{u}(x,k_y,z) + 2 k_y^2\,\sigma\,\tilde{u}(x,k_y,z) &= s(x,y,z).
\end{align}
The 3d solution on the $xz$-plane is thus
\begin{align}
u(x,y=0,z) &= \frac{2}{\pi}\int_0^\infty \tilde{u}\,{\rm d}k_y.
\end{align}
Discretized, we have
\begin{align}
u = \frac{2}{\pi}\sum_i \tilde{u}(k_{i})\,\omega_i,
\label{eqn:u-uky}
\end{align}
but what are $k_{i}$ and $\omega_i$? We follow \cite{pidlisecky2008fw2_5d} and proceed to find them by noting that the Green's function solution (for homogeneous $\sigma$) of (\ref{eqn:dc-2-5d}) on the half $xz$-plane is 
\begin{align}
u(x,y=0,z) &= \frac{{\bf i}}{2\pi\sigma}
\underbrace{\left(\frac{1}{\underbrace{||x-s_+||_2}_{r+}} - \frac{1}{\underbrace{||x-s_-||_2}_{r-}}\right)}_{1/R},
\label{eqn:u-solu}
\end{align}
bringing back to the Fourier domain,
\begin{align}
\tilde{u} &= \int_0^\infty u\,\cos(y\,k_y)\;{\rm d}y = \frac{{\bf i}}{2\pi\sigma}(B_o(k_y r_{+}) - B_o(k_y r_{-})),
\label{eqn:uky-solu}
\end{align}
where $B_o$ is the zero order modified Bessel function of the second kind. By plugging in equations \ref{eqn:u-solu} and \ref{eqn:uky-solu} into equation \ref{eqn:u-uky} we discretize by 
\begin{align}
1&\approx \sum_j \, \underbrace{\frac{2R}{\pi}\{B_o(k_j\,r_+) - B_o(k_j\,r_-)\}}_{K_{ij}} \,\omega_j \\
K &= \frac{2}{\pi}R\left\{ B_o(k\,r_+) - B_o(k\,r_-) \right\} \\
v &= K\omega,
\label{eqn:Kwv}
\end{align}
where $K=K(k,\,s)$ is a matrix of size $(n_R\times n_k)$, $v$ is a vector of length $n_R$ whose entries should approximate $1$, and $k=(k_{i})$, $\omega=(\omega_i)$ are vectors of length $n_k$. We minimize
\[
\Phi(k) = || 1 - \underbrace{K\underbrace{(K^TK)^{-1}K^T}_{\omega}}_{v(k)} ||_2^2 = 
||1-v(k)||_2^2,
\]
using a regularized Newton method. Note that both $k$ and $\omega$ are geometry dependent and not parameter dependent.
\subsection*{Finding $k_y$ and $\omega$ for a given $s$}
\begin{enumerate}
\item initial guess for $k=(\text{some numbers})\cdot\Delta x$ and build $K(k,s)$.
\item $v\gets K(K^\top K)^{-1}K^\top \cdot 1$,
\item compute $J=\nabla_k v$ using $n_k$ finite differences,
\item $ \nabla_k \Phi^\top \gets J^\top(1-v)+\beta k$,
\item $\Delta k = (J^\top J+\beta I)^{-1}\cdot \nabla_k \Phi^\top$,
\item $k\gets k+\alpha\,\Delta k$,
\item build $K(k,s)$
\item check if $v$ is almost $1$, 
\item repeat $2-8$
\item $\omega=(K^\top K)^{-1}K^\top \cdot 1$,
\item \color{red}correct for flatness $k\gets k\cdot\Delta x$ \color{black}
\item return $k$ and $\frac{2}{\pi}\omega$.
\end{enumerate}
%
\subsection*{Finding the 2.5d electric potential $u$ for given $s$ and $\sigma$}
Given a source $s$ and conductivity $\sigma$, the forward model is computed as follows,
\begin{enumerate}
\item retrieve from memory (or compute) $k$ and $\omega$,
\item choose $k_i\in k$ and build $L_i$ with the right boundary conditions for that $k_i$,
\begin{align*}
L^{i} &\approx -\nabla\cdot\sigma\nabla,\\
L_{i} &= L^{i} + k_i^2\,\sigma,
\end{align*}
\item solve $L_{i}\tilde{u}_{i}=\frac{s}{2}$ for $\tilde{u}_{i}$ and store,
\item repeat 3-4 until all $k$ has been used,
\item $u=\sum_i \omega_i \,\tilde{u}_{i} \to d=Mu \to e=d-d^o$.
\end{enumerate}
% ----------------
% 2.5d inversion
% ----------------
\section*{2.5d inversion}
Each 2d forward model is,
\begin{align*}
L_{i} &= L^{i} + k_i^2\,\sigma, \\
L_{i} \tilde{u}_{i} &= \frac{s}{2}, \\
\tilde{d}_{i} &= M\tilde{u}_{i}.
\end{align*}
We can write the 2.5d data and its Jacobian as a linear combination of each 2d problem,
\begin{align*}
d &= M\underbrace{\sum_i \omega_i \tilde{u}_i}_{u} = \sum_i \omega_i \underbrace{M\tilde{u}_i}_{\tilde{d}_i} = \sum_i \omega_i \tilde{d}_i, \\
\nabla_\sigma d &= \underbrace{\sum_i \omega_i J_i}_{J},
\end{align*}
where
\begin{align*}
J_i &= ML_i^{-1}S_i^{\top}, \hspace{2em}\text{and}\hspace{2em}
S_i = -\left( (\nabla_\sigma L^i)\tilde{u}_i \right)^{\top} - k_i^2 \; \mbox{diag}(\tilde{u}_i)^{\top}.
\end{align*}
We can now write the gradient of the 2.5d data as a linear combination of the 2d gradients,
\begin{align*}
g &= \left( \sum_i \omega_i J_i \right)^\top e = \sum_i \omega_i \underbrace{J_i^\top e}_{g_i} = 
\sum_i \omega_i g_i, 
\end{align*}
where
\begin{align*}
g_i &= S_i a_i, \hspace{2em}\text{and}\hspace{2em}
L_i^{\top}a_i = M^\top e.
\end{align*}
%i
\subsection*{Finding $g$ for given $s$ and $\sigma$}
Given a source $s$, conductivity $\sigma$ and weights $\{k,\omega\}$ the gradient is computed as follows,
\begin{enumerate}
\item compute the 2.5d forward model to get $\{\tilde{u}_{i}\}$ and $e$,
\item choose $k_i\in k$,
\item build $L_{i}$ and $S_{i} = -\left( (\nabla_\sigma L^i)\tilde{u}_{i} \right)^{\top} - k_i^2\; \mbox{diag}(\tilde{u}_{i})^{\top}$,
\item solve $L_{i}^{\top}a_{i} = M^\top e$ for $a_{i}$,
\item compute and store $g_{i} = S_{i} a_{i}$,
\item repeat 2-5 until all $k$ has been used,
\item $g=\sum_i \omega_i \,g_{i}$.
\end{enumerate}
%
\section*{Routines}
\begin{itemize}
\item \color{boiseBlue}\texttt{dc\_kfourier.m} \color{black} for given source $s$ outputs $\{k,\omega\}$.
\item \color{boiseBlue}\texttt{dc\_fwd2\_5d.m} \color{black} for a given source $s$ and for each $k_i\in k$ performs \color{rojoAmor}\texttt{dc\_fwd\_k.m} \color{black} and solves $u$ by weight-stacking $\{\tilde{u}_{k_i}\}$. Outputs $L$, $u$, $\{\tilde{u}_{k_i}\}$, $d=Mu$ and $e=d-d^o$.
%
\begin{itemize}
\item[\textbullet] \color{rojoAmor}\texttt{dc\_fwd\_k.m} \color{black} for a given source $s$ and a given $k_i\in k$ solves the 2d fwd problem $L_{k_i}\tilde{u}_{k_i}=s$. Outputs $L$ and $\tilde{u}_{k_i}$.
\end{itemize}
%
\item \color{boiseBlue}\texttt{dc\_gradient2\_5d.m} \color{black} for a given source $s$, its weights $\{k,\omega\}$, its 2d potentials $\{\tilde{u}_{k_i}\}$, its matrix $L$ and its 2.5d error $e$, outputs $g$ as a weighted stack of $\{g_{k_i}\}$.
\end{itemize}
%
\section*{Verification with analytical models}
anal-homo and anal-bi.
%
%
%------------
% biblio
%------------
%\newpage
\bibliographystyle{plainnat}
\bibliography{2d-25d}
%\nocite{*}
\end{document}